### 2014-07-25 Docs/FAQ/faq.tex

>>>>

\item {\em How can I debug a parallel (MPI) job with gdb?}

If you only need to use a few processors, the following command will work:
\begin{verbatim}
mpiexec -n 4 xterm -e gdb ./main.Linux.gfortran.mpi.exe 
\end{verbatim}
where the executable needs to be created with the ``{\tt -g}'' flag to
the compiler.  This will pop up multiple {\tt xterm}s with {\tt gdb} running
in each.  You need to then issue:
\begin{verbatim}
run inputs
\end{verbatim}
where {\tt inputs} is the desired inputs file {\em in each} {\tt xterm}.

### 2014-07-25 Docs/mg/mg.tex

Here we describe some of the general ideas behind the \boxlib\ multigrid.

@@

@@

There are two MG solvers: cell-centered and nodal.

>>>>

Here we describe some of the general ideas behind the \boxlib\
multigrid (MG).

@@

The MG solvers are located in {\tt BoxLib/Src/LinearSolvers/F\_MG/}.
There are two MG solvers, for cell-centered and nodal data.
Generally, the routines specific to the cell-centered solver will have
{\tt cc} in their name, and those specific to the nodal solver will have
{\tt nd} in their name.

@@
